Empirical Research Paper Project

### 2019-12-14 content/assignment/paper-project.Rmd
Change github logo link on empirical example

- [<i class="fas fa-external-link-square-alt"></i> Writing and Reading Empirical Papers Slides](/slides/paper-slides.html)

>>>>

- [<i class="fas fa-external-link-square-alt"></i> Writing and Reading Empirical Papers Slides](/slides/paper-slides.html)
- [<i class="fab fa-github"></i> Example Paper Project](https://github.com/ryansafner/example_empirical_paper)
